An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-06-02 tex/paper.tex
Correcting KML's affiliation.
Correcting Marc's name.
Correcting KMLs name in contrib list.
New title.
Resizing smaller images.

An open reproducible framework for the study of the iterated prisoner's
dilemma.

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
        % Core devs (alphabetic order of last name after Vince as corresponding
        % goes first).
        \item Knight, Vincent
        \item Campbell, Owen
        \item Harper, Marc
        \item Langner, Karol
        % All devs (alphabetic order of last name)
        \item Campbell, James
        \item Campbell, Thomas
        \item Carney, Alex
        \item Chorley, Martin
        \item Davidson-Pilon, Cameron
        \item Glass, Kristian
        \item Ehrlich Tom{\'a}{\v s}
        \item Jones, Martin
        \item Koutsovoulos, Georgios
        \item Tibble, Holly
        \item M{\"u}ller, Jochen
        \item Palmer, Geraint
        \item Slavin, Paul
        \item Standen, Timothy
        \item Visintini, Luis
        \item Molden, Karl
    \end{enumerate}
\end{multicols}

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Cardiff University
\item Development; St. Nicholas Catholic High School, Hartford
\item Development; Cardiff University
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; The University of Edinburgh
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Cardiff University
\item Development; The University of Manchester
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
    \end{enumerate}
\end{multicols}

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=.75\textwidth]{demo_tournament.pdf}
        \caption{The results from a simple tournament.}
        \label{fig:demo_tournament}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=.75\textwidth]{stewart_tournament.pdf}
        \caption{The results from \cite{Stewart2012}.}
        \label{fig:stewart_tournament}
    \end{subfigure}
    \caption{Summary plots produced by the library.}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=.75\textwidth]{outline_of_library.pdf}
        \caption{An overview of the source code.}
        \label{fig:overview}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{number_of_strategies_with_arima_projection.pdf}
        \caption{The number of strategies included in the library}
        \label{fig:number_of_strategies_against_date}
    \end{subfigure}
    \caption{An overview of the library.}
\end{figure}

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
previous research being done in an irreproducible manner with, for example, no
source code and/or vaguely described strategies, not all previous tournaments
can yet be reproduced. In fact, some of the early tournaments might be
impossible to reproduce as the source code is forever lost. This library aims
to prevent this from happening again in the future.

@@

@@

\begin{multicols}{2}
    \begin{itemize}[noitemsep,topsep=0pt]
        \item {Owen Campbell}
        \item {Mark Harper}
        \item {Vincent Knight}
        \item {Karol Langner}
        \item {James Campbell}
        \item {Thomas Campbell}
        \item {Alex Carney}
        \item {Martin Chorley}
        \item {Cameron Davidson-Pilon}
        \item {Kristian Glass}
        \item {Tom{\'a}{\v s} Ehrlich}
        \item {Martin Jones}
        \item {Georgios Koutsovoulos}
        \item {Marissa Tibble}
        \item {Jochen M{\"u}ller}
        \item {Geraint Palmer}
        \item {Paul Slavin}
        \item {Timothy Standen}
        \item {Luis Visintini}
        \item {Karl Molden}
        \item {Jason Young}
        \item {Andy Boot}
        \item {Anna Barriscale}
    \end{itemize}
\end{multicols}

>>>>

An open framework for the reproducible study of the iterated prisoner's
dilemma.

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
        % Core devs (alphabetic order of last name after Vince as corresponding
        % goes first).
        \item Knight, Vincent
        \item Campbell, Owen
        \item Harper, Marc
        \item Langner, Karol M.
        % All devs (alphabetic order of last name)
        \item Campbell, James
        \item Campbell, Thomas
        \item Carney, Alex
        \item Chorley, Martin
        \item Davidson-Pilon, Cameron
        \item Glass, Kristian
        \item Ehrlich Tom{\'a}{\v s}
        \item Jones, Martin
        \item Koutsovoulos, Georgios
        \item Tibble, Holly
        \item M{\"u}ller, Jochen
        \item Palmer, Geraint
        \item Slavin, Paul
        \item Standen, Timothy
        \item Visintini, Luis
        \item Molden, Karl
    \end{enumerate}
\end{multicols}

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Google Inc., Mountain View, CA
\item Development; Cardiff University
\item Development; St. Nicholas Catholic High School, Hartford
\item Development; Cardiff University
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; The University of Edinburgh
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Cardiff University
\item Development; The University of Manchester
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
    \end{enumerate}
\end{multicols}

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.75\textwidth]{demo_tournament.pdf}
	\caption{The results from a simple tournament.}
	\label{fig:demo_tournament}
\end{figure}

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.9\textwidth]{outline_of_library.pdf}
	\caption{An overview of the source code.}
	\label{fig:overview}
\end{figure}

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}.

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.75\textwidth]{number_of_strategies_with_arima_projection.pdf}
	\caption{The number of strategies included in the library}
	\label{fig:number_of_strategies_against_date}
\end{figure}

Despite this, due to previous research being done in an irreproducible manner
with, for example, no source code and/or vaguely described strategies, not all
previous tournaments can yet be reproduced. In fact, some of the early
tournaments might be impossible to reproduce as the source code is forever
lost. This library aims to prevent this from happening again in the future.

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.75\textwidth]{stewart_tournament.pdf}
	\caption{The results from \cite{Stewart2012}.}
	\label{fig:stewart_tournament}
\end{figure}

@@

\begin{multicols}{2}
    \begin{itemize}[noitemsep,topsep=0pt]
        \item {Owen Campbell}
        \item {Marc Harper}
        \item {Vincent Knight}
        \item {Karol M. Langner}
        \item {James Campbell}
        \item {Thomas Campbell}
        \item {Alex Carney}
        \item {Martin Chorley}
        \item {Cameron Davidson-Pilon}
        \item {Kristian Glass}
        \item {Tom{\'a}{\v s} Ehrlich}
        \item {Martin Jones}
        \item {Georgios Koutsovoulos}
        \item {Marissa Tibble}
        \item {Jochen M{\"u}ller}
        \item {Geraint Palmer}
        \item {Paul Slavin}
        \item {Timothy Standen}
        \item {Luis Visintini}
        \item {Karl Molden}
        \item {Jason Young}
        \item {Andy Boot}
        \item {Anna Barriscale}
    \end{itemize}
\end{multicols}
